### 2019-03-19 papers/journal/experiments.tex
exmaple update

%Each completed graph is a prediction of our model. For every single incomplete graph, there are multiple ways to complete it, although, in this paper, we output the minimum number of changes required to complete the input graph.
%%
%These results are intended to be used as guides for further discoveries, where the predicted new vesicles and molecular components of existing vesicles and compartments can be tested experimentally.
The biological VTS graphs known to date are incomplete in the sense that we do not know all the edges, and we also do not know all the molecules that populate the edges and the nodes of the VTS.
%%
These queries represent different levels of changes that we can make in order to complete these graphs.
%
Each completed graph is a prediction of our model. 
%
For every single incomplete graph, there are multiple ways to complete it, although, in this paper, we output the minimum number of changes required to complete the input graph. 
%
These results are intended to be used as guides for further discoveries, where the predicted new vesicles and molecular components of existing vesicles and compartments can be tested experimentally.
%
%Our experiments suggest that the synthesis problems are solvable by modern 
%solvers and the synthesis technology may be useful for biological research.
%

>>>>

%Each completed graph is a prediction of our model. For every single incomplete graph, there are multiple ways to complete it, although, in this paper, we output the minimum number of changes required to complete the input graph.
%%
%These results are intended to be used as guides for further discoveries, where the predicted new vesicles and molecular components of existing vesicles and compartments can be tested experimentally.
%The biological VTS graphs known to date are incomplete in the sense that we do not know all the edges, and we also do not know all the molecules that populate the edges and the nodes of the VTS.
%%
Biologically, these queries represent different levels of changes that we can make in order to complete these graphs.
%
Each completed graph is a prediction of our model. 
%
For every single incomplete graph, there are multiple ways to complete it, although, in this paper, we output the minimum number of changes required to complete the input graph. 
%
These results are intended to be used as guides for further discoveries, where the predicted new vesicles and molecular components of existing vesicles and compartments can be tested experimentally.
%
%Our experiments suggest that the synthesis problems are solvable by modern 
%solvers and the synthesis technology may be useful for biological research.
%
